---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://img.shields.io/badge/lifecycle-experimental-orange.svg)


# {trycatchthis}

A friendlier trycatch for R, based on {purrr} mappers.

## Example

You can write a try catch with these params : 

+ `...` the expression to be evaluated 
+ `.e` a one side formula or a function evaluated when an error occurs
+ `.w` a one side formula or a function evaluated when a warning occurs
+ `.f` a one side formula or an expression which is always evaluated before returning or exiting

### With mappers 

```{r}
library(trycatchthis)
try_catch(log("a"), 
          .e = ~ paste0("There is an error: ", .x), 
          .w = ~ paste0("This is a warning: ", .x))

try_catch(log("a"), 
          .e = ~ print(.x), 
          .w = ~ print(.x))

try_catch(matrix(1:3, nrow= 2), 
          .e = ~ print(.x), 
          .w = ~ print(.x))

try_catch(2 + 2 , 
          .f = ~ print("Using R for addition... ok I'm out!"))
```

### Traditionnal way 

{trycatchthis} is flexible in how you can specify your arguments. 

You can, as you do with {base} `tryCatch`, use a plain old function: 

```{r}
try_catch(log("a"), 
          .e = function(e){
            print(paste0("There is an error: ", e))
            print("Ok, let's save this")
            time <- Sys.time()
            a <- paste("+ At",time, ", \nError:",e)
            # write(a, "log.txt", append = TRUE) # commented to prevent from log.txt creation on your machine
            print(paste("log saved on log.txt at", time))
          }, 
          .f = ~ print("let's move on now"))
```

Or even mix both: 

```{r}
try_catch(log("a"), 
          .e = function(e){
            paste0("There is an error: ", e)
          },
          .f = ~ print("I'm not sure you can do that pal !"))
```

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
